The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-11 papers/pair-correlation/paper.tex

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Make note of the double curves}\fixme{Add backward curve for
      this work mc?}\pahosays{would annotations be clearer if they were on the
      x/z ticks instead of arrows?}The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when $\rr_1$
    and $\rr_2$ are in contact.  The color plot on the left shows the triplet
    distribution function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows the value of
    $g^{(3)}$ along the path shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Make note of the double curves}\fixme{Add backward curve for
      this work mc?}The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when $\rr_1$
    and $\rr_2$ are in contact.  The color plot on the left shows the triplet
    distribution function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows the value of
    $g^{(3)}$ along the path shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}
